---
title: "Constant_Depth"
author: "Hannah Curtis"
date: "2024-01-29"
output: html_document
---
This file calculates various hydrologic variables associated with the percentage of time the water level is at or between certain locations. The variables include median water level, percentage of time water level is within 2 inches of the mode, percentage of time water level is within 6 inches of the mode, percentage of time water level is within 6 inches of the outlet, percentage of time water level is below the outlet, the range of water levels between the 25th and 75th percentile, the range of water levels between the 10th and 90th percentile, and the skewness of the water level pdfs.

Updated: 8/14/24 to include 2024 data

Read in water level files
```{r}
baxter_wl <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/Baxter/Baxter_Water_Level_all.csv")
commave_wl <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/CommAve/CommAve_Water_Level_all.csv")
doba4_wl <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/DobA4/DobA4_Water_Level_all_corrected.csv")
doba5_wl <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/DobA5/DobA5_Water_Level_all.csv")
doba7_wl <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/DobA7/DobA7_Water_Level_all.csv")
doba8_wl <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/DobA8/DobA8_Water_Level_all.csv")
doba22_wl <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/DobA22/DobA22_Water_Level_all.csv")
doorcreek_wl <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/DoorCreek/DoorCreek_Water_Level_all.csv")
elver_wl <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/Elver/Elver_Water_Level_all.csv")
garner_wl <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/Garner/Garner_Water_Level_all.csv")
greentree_wl <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/Greentree/Greentree_Water_Level_all.csv")
hospital_wl <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/Hospital/Hospital_Water_Level_all.csv")
hpchurch_wl <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/HPChurch/HPChurch_Water_Level.csv")
lot60_wl <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/Lot60/Lot60_Water_Level_all.csv")
madcity_wl <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/MadCity/MadCity_Water_Level_all.csv")
manitou_wl <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/Manitou/Manitou_Water_Level_all.csv")
mariondunn_wl <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/MarionDunn/MarionDunn_Water_Level_all.csv")
midtown_wl <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/Midtown/Midtown_Water_Level_all.csv")
owen_wl <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/Owen/Owen_Water_Level_all.csv")
twofountains_wl <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/TwoFountains/TwoFountains_Water_Level_all.csv")
```

WL Histograms
```{r}
plot_histd <- function(pond_depth, color, name) {
  hist(pond_depth, probability=TRUE, breaks=100, xlim=c(0,5), main=paste(name), xlab="Water Level (ft)", ylab="Density", col=color, border=color)
  lines(density(pond_depth),col="black",lwd=2)
  grid() 
  box()
}

bax_histd <- plot_histd(na.omit(baxter_wl$Depth.ft), "dodgerblue4", "Baxter") 
comm_histd <- plot_histd(na.omit(commave_wl$Depth.ft), "red", "Commercial Ave") 
da4_histd <- plot_histd(na.omit(doba4_wl$Depth.ft), "green", "Dobson A4") 
da5early_histd <- plot_histd(doba5_wl$Depth.ft, "gold", "Dobson A5") 
da7_histd <- plot_histd(na.omit(doba7_wl$Depth.ft), "magenta", "Dobson A7") 
da8_histd <- plot_histd(na.omit(doba8_wl$Depth.ft), "orange", "Dobson A8") 
da22_histd <- plot_histd(na.omit(doba22_wl$Depth.ft), "gray", "Dobson A22") 
dc_histd <- plot_histd(na.omit(doorcreek_wl$Depth.ft), "purple", "Door Creek") 
elver_histd <- plot_histd(na.omit(elver_wl$Depth.ft), "brown", "Elver") 
gar_histd <- plot_histd(na.omit(garner_wl$Depth.ft), "skyblue", "Garner")
gt_histd <- plot_histd(na.omit(greentree_wl$Depth.ft), "coral1", "Greentree")
hos_histd <- plot_histd(na.omit(hospital_wl$Depth.ft), "lavender", "Hospital") 
hp_histd <- plot_histd(na.omit(hpchurch_wl$Depth.ft), "forestgreen", "High Point Church") 
l60_histd <- plot_histd(na.omit(lot60_wl$Depth.ft), "yellow", "Lot 60") 
mc_histd <- plot_histd(na.omit(madcity_wl$Depth.ft), "maroon", "Mad City")
man_histd <- plot_histd(na.omit(manitou_wl$Depth.ft), "pink", "Manitou") 
md_histd <- plot_histd(na.omit(mariondunn_wl$Depth.ft), "royalblue", "Marion Dunn")
mid_histd <- plot_histd(midtown_wl$Depth.ft, "lightsalmon", "Midtown")
owen_histd <- plot_histd(na.omit(owen_wl$Depth.ft), "tan", "Owen") 
tf_histd <- plot_histd(na.omit(twofountains_wl$Depth.ft), "darkgray", "Two Fountains") 
```

Histogram Results
```{r}
# Create histogram and store the result
bax_hist <- hist(baxter_wl$Depth.ft, breaks = 100, plot = FALSE)
# Find the index of the bin with the highest count
max_count_index <- which.max(bax_hist$counts)
# Get the count of the highest bin
max_count <- bax_hist$counts[max_count_index]
# Get the range of the bin with the highest count
max_bin_range <- c(bax_hist$breaks[max_count_index], bax_hist$breaks[max_count_index + 1])
print(max_bin_range)
```

Median water level
```{r}
# Median water level
baxter_med <- median(baxter_wl$Depth.ft)
commave_med <- median(commave_wl$Depth.ft)
doba4_med <- median(doba4_wl$Depth.ft)
doba5_med <- median(doba5_wl$Depth.ft)
doba7_med <- median(doba7_wl$Depth.ft)
doba8_med <- median(doba8_wl$Depth.ft)
doba22_med <- median(doba22_wl$Depth.ft)
doorcreek_med <- median(doorcreek_wl$Depth.ft)
elver_med <- median(elver_wl$Depth.ft)
garner_med <- median(garner_wl$Depth.ft)
greentree_med <- median(na.omit(greentree_wl$Depth.ft))
hospital_med <- median(hospital_wl$Depth.ft)
hpchurch_med <- median(na.omit(hpchurch_wl$Depth.ft))
lot60_med <- median(lot60_wl$Depth.ft)
madcity_med <- median(madcity_wl$Depth.ft)
manitou_med <- median(manitou_wl$Depth.ft)
mariondunn_med <- median(mariondunn_wl$Depth.ft)
midtown_med <- median(midtown_wl$Depth.ft)
owen_med <- median(owen_wl$Depth.ft)
twofountains_med <- median(twofountains_wl$Depth.ft)

# Save median water level variable
median_wl <- c(hospital_med,lot60_med,garner_med,doba7_med,owen_med,hpchurch_med,doba8_med,midtown_med,elver_med,twofountains_med,greentree_med,mariondunn_med,manitou_med,madcity_med,baxter_med,doba22_med,doba5_med,doba4_med,doorcreek_med,commave_med)

```

Percentage of days water level is within 2 inches of mode in each pond
```{r}
# Function for percentage of days water level is roughly constant
get_const_wl <- function(pond_wl, mode_wl) {
  # one inch below most common water level
  wl_min <- mode_wl - 1/12
  # one inch above below most common water level
  wl_max <- mode_wl + 1/12
  # get the water levels within 2 inches of the most common water level
  filtered_wl <- pond_wl[pond_wl >= wl_min & pond_wl <= wl_max]
  # find percentage of days water level is within this range
  percentage_const_wl <- (length(filtered_wl)/length(pond_wl))*100
  return(percentage_const_wl)
}

# Apply function to each pond
baxter_const_wl <- get_const_wl(baxter_wl$Depth.ft, 0.325)
commave_const_wl <- get_const_wl(commave_wl$Depth.ft, 1.625)
doba4_const_wl <- get_const_wl(doba4_wl$Depth.ft, 1.525)
doba5_const_wl <- get_const_wl(doba5_wl$Depth.ft, 1.675)
doba7_const_wl <- get_const_wl(doba7_wl$Depth.ft, 0.675)
doba8_const_wl <- get_const_wl(doba8_wl$Depth.ft, 2.225)
doba22_const_wl <- get_const_wl(doba22_wl$Depth.ft, 0.15)
doorcreek_const_wl <- get_const_wl(doorcreek_wl$Depth.ft, 1.43)
elver_const_wl <- get_const_wl(elver_wl$Depth.ft, 1.675)
garner_const_wl <- get_const_wl(garner_wl$Depth.ft, 1.475)
greentree_const_wl <- get_const_wl(na.omit(greentree_wl$Depth.ft), 1.425)
hospital_const_wl <- get_const_wl(hospital_wl$Depth.ft, 1.175)
hpchurch_const_wl <- get_const_wl(hpchurch_wl$Depth.ft, 1.425)
lot60_const_wl <- get_const_wl(lot60_wl$Depth.ft, 1.91)
madcity_const_wl <- get_const_wl(madcity_wl$Depth.ft, 1.825)
manitou_const_wl <- get_const_wl(manitou_wl$Depth.ft, 0.875)
mariondunn_const_wl <- get_const_wl(mariondunn_wl$Depth.ft, 1.625)
midtown_const_wl <- get_const_wl(midtown_wl$Depth.ft, 2.425)
owen_const_wl <- get_const_wl(owen_wl$Depth.ft, 2.025)
twofountains_const_wl <- get_const_wl(twofountains_wl$Depth.ft, 1.73)

# Save percentage of days water level is roughly constant as variable
constant_wl <- c(hospital_const_wl,lot60_const_wl,garner_const_wl,doba7_const_wl,owen_const_wl,hpchurch_const_wl,doba8_const_wl,midtown_const_wl,elver_const_wl,twofountains_const_wl,greentree_const_wl,mariondunn_const_wl,manitou_const_wl,madcity_const_wl,baxter_const_wl,doba22_const_wl,doba5_const_wl,doba4_const_wl,doorcreek_const_wl,commave_const_wl)
```

Percentage of days water level is within 6 inches of mode in each pond
```{r}
# Function for percentage of days water level is roughly constant
get_const_wl_6in <- function(pond_wl, mode_wl) {
  # three inches below most common water level
  wl_min <- mode_wl - 3/12
  # three inches above below most common water level
  wl_max <- mode_wl + 3/12
  # get the water levels within 6 inches of the most common water level
  filtered_wl <- pond_wl[pond_wl >= wl_min & pond_wl <= wl_max]
  # find percentage of days water level is within this range
  percentage_const_wl <- (length(filtered_wl)/length(pond_wl))*100
  return(percentage_const_wl)
}

# Apply function to each pond
baxter_const_wl_6in <- get_const_wl_6in(baxter_wl$Depth.ft, 0.325)
commave_const_wl_6in <- get_const_wl_6in(commave_wl$Depth.ft, 1.625)
doba4_const_wl_6in <- get_const_wl_6in(doba4_wl$Depth.ft, 1.525)
doba5_const_wl_6in <- get_const_wl_6in(doba5_wl$Depth.ft, 1.675)
doba7_const_wl_6in <- get_const_wl_6in(doba7_wl$Depth.ft, 0.675)
doba8_const_wl_6in <- get_const_wl_6in(doba8_wl$Depth.ft, 2.225)
doba22_const_wl_6in <- get_const_wl_6in(doba22_wl$Depth.ft, 0.15)
doorcreek_const_wl_6in <- get_const_wl_6in(doorcreek_wl$Depth.ft, 1.43)
elver_const_wl_6in <- get_const_wl_6in(elver_wl$Depth.ft, 1.675)
garner_const_wl_6in <- get_const_wl_6in(garner_wl$Depth.ft, 1.475)
greentree_const_wl_6in <- get_const_wl_6in(na.omit(greentree_wl$Depth.ft), 1.425)
hospital_const_wl_6in <- get_const_wl_6in(hospital_wl$Depth.ft, 1.175)
hpchurch_const_wl_6in <- get_const_wl_6in(hpchurch_wl$Depth.ft, 1.425)
lot60_const_wl_6in <- get_const_wl_6in(lot60_wl$Depth.ft, 1.91)
madcity_const_wl_6in <- get_const_wl_6in(madcity_wl$Depth.ft, 1.825)
manitou_const_wl_6in <- get_const_wl_6in(manitou_wl$Depth.ft, 0.875)
mariondunn_const_wl_6in <- get_const_wl_6in(mariondunn_wl$Depth.ft, 1.625)
midtown_const_wl_6in <- get_const_wl_6in(midtown_wl$Depth.ft, 2.425)
owen_const_wl_6in <- get_const_wl_6in(owen_wl$Depth.ft, 2.025)
twofountains_const_wl_6in <- get_const_wl_6in(twofountains_wl$Depth.ft, 1.73)

# Save percentage of days water level is roughly constant as variable
constant_wl_6in <- c(hospital_const_wl_6in,lot60_const_wl_6in,garner_const_wl_6in,doba7_const_wl_6in,owen_const_wl_6in,hpchurch_const_wl_6in,doba8_const_wl_6in,midtown_const_wl_6in,elver_const_wl_6in,twofountains_const_wl_6in,greentree_const_wl_6in,mariondunn_const_wl_6in,manitou_const_wl_6in,madcity_const_wl_6in,baxter_const_wl_6in,doba22_const_wl_6in,doba5_const_wl_6in,doba4_const_wl_6in,doorcreek_const_wl_6in,commave_const_wl_6in)
```

Percentage of days water level is within 6 inches of outlet in each pond
```{r}
# Function for percentage of days water level is within 6in of the outlet
get_outlet_wl <- function(pond_wl, outlet_wl) {
  # one inch below most common water level
  wl_min <- outlet_wl - 3/12
  # one inch above below most common water level
  wl_max <- outlet_wl + 3/12
  # get the water levels within 6 inches of outlet
  filtered_wl <- pond_wl[pond_wl >= wl_min & pond_wl <= wl_max]
  # find percentage of days water level is within this range
  percentage_const_wl <- (length(filtered_wl)/length(pond_wl))*100
  return(percentage_const_wl)
}

# Apply function to each pond
baxter_outlet_wl <- get_outlet_wl(baxter_wl$Depth.ft, 11/12)
commave_outlet_wl <- get_outlet_wl(commave_wl$Depth.ft, 17.5/12)
doba4_outlet_wl <- get_outlet_wl(doba4_wl$Depth.ft, 14.5/12)
doba5_outlet_wl <- get_outlet_wl(doba5_wl$Depth.ft, 15.5/12)
doba7_outlet_wl <- get_outlet_wl(doba7_wl$Depth.ft, 12/12)
doba8_outlet_wl <- get_outlet_wl(doba8_wl$Depth.ft, 24/12)
doba22_outlet_wl <- get_outlet_wl(doba22_wl$Depth.ft, 5.29)
doorcreek_outlet_wl <- get_outlet_wl(doorcreek_wl$Depth.ft, 3.5/12) # check
elver_outlet_wl <- get_outlet_wl(elver_wl$Depth.ft, 20.5/12)
garner_outlet_wl <- get_outlet_wl(garner_wl$Depth.ft, 14/12)
greentree_outlet_wl <- get_outlet_wl(na.omit(greentree_wl$Depth.ft), 14.5/12)
hospital_outlet_wl <- get_outlet_wl(hospital_wl$Depth.ft, 18/12) # check
hpchurch_outlet_wl <- get_outlet_wl(hpchurch_wl$Depth.ft, 18/12) # check
lot60_outlet_wl <- get_outlet_wl(lot60_wl$Depth.ft, 3.5/12)
madcity_outlet_wl <- get_outlet_wl(madcity_wl$Depth.ft, 10/12)
manitou_outlet_wl <- get_outlet_wl(manitou_wl$Depth.ft, 8.5/12)
mariondunn_outlet_wl <- get_outlet_wl(mariondunn_wl$Depth.ft, 7/12)
midtown_outlet_wl <- get_outlet_wl(midtown_wl$Depth.ft, 27.25/12)
owen_outlet_wl <- get_outlet_wl(owen_wl$Depth.ft, 2.5) # check
twofountains_outlet_wl <- get_outlet_wl(twofountains_wl$Depth.ft, 16/12)

# Save percentage of days water level is within 6in of outlet as variable
outlet_wl <- c(hospital_outlet_wl,lot60_outlet_wl,garner_outlet_wl,doba7_outlet_wl,owen_outlet_wl,hpchurch_outlet_wl,doba8_outlet_wl,midtown_outlet_wl,elver_outlet_wl,twofountains_outlet_wl,greentree_outlet_wl,mariondunn_outlet_wl,manitou_outlet_wl,madcity_outlet_wl,baxter_outlet_wl,doba22_outlet_wl,doba5_outlet_wl,doba4_outlet_wl,doorcreek_outlet_wl,commave_outlet_wl)
```

Percentage of days water level is above/below outlet in each pond
```{r}
# Function for percentage of days water level is below outlet
get_below_outlet_wl <- function(pond_wl, outlet_wl) {
  # get the water levels below the outlet location
  filtered_wl <- pond_wl[pond_wl < outlet_wl]
  # find percentage of days water level is within this range
  percentage_below_outlet_wl <- (length(filtered_wl)/length(pond_wl))*100
  return(percentage_below_outlet_wl)
}

# Apply function to each pond
baxter_below_outlet_wl <- get_below_outlet_wl(baxter_wl$Depth.ft, 12/12)
commave_below_outlet_wl <- get_below_outlet_wl(commave_wl$Depth.ft, 17.5/12)
doba4_below_outlet_wl <- get_below_outlet_wl(doba4_wl$Depth.ft, 19.5/12/12)
doba5_below_outlet_wl <- get_below_outlet_wl(doba5_wl$Depth.ft, 15.5/12)
doba7_below_outlet_wl <- get_below_outlet_wl(doba7_wl$Depth.ft, 12/12)
doba8_below_outlet_wl <- get_below_outlet_wl(doba8_wl$Depth.ft, 25/12)
doba22_below_outlet_wl <- get_below_outlet_wl(doba22_wl$Depth.ft, 66.6/12)
doorcreek_below_outlet_wl <- get_below_outlet_wl(doorcreek_wl$Depth.ft, 18/12) # check
elver_below_outlet_wl <- get_below_outlet_wl(elver_wl$Depth.ft, 20.5/12)
garner_below_outlet_wl <- get_below_outlet_wl(garner_wl$Depth.ft, 14/12)
greentree_below_outlet_wl <- get_below_outlet_wl(na.omit(greentree_wl$Depth.ft), 17/12)
hospital_below_outlet_wl <- get_below_outlet_wl(hospital_wl$Depth.ft, 17/12) # check
hpchurch_below_outlet_wl <- get_below_outlet_wl(hpchurch_wl$Depth.ft, 12/12) # check
lot60_below_outlet_wl <- get_below_outlet_wl(lot60_wl$Depth.ft, 16.5/12)
madcity_below_outlet_wl <- get_below_outlet_wl(madcity_wl$Depth.ft, 22/12)
manitou_below_outlet_wl <- get_below_outlet_wl(manitou_wl$Depth.ft, 8/12)
mariondunn_below_outlet_wl <- get_below_outlet_wl(mariondunn_wl$Depth.ft, 14/12)
midtown_below_outlet_wl <- get_below_outlet_wl(midtown_wl$Depth.ft, 27.25/12)
owen_below_outlet_wl <- get_below_outlet_wl(owen_wl$Depth.ft, 3.25) # check
twofountains_below_outlet_wl <- get_below_outlet_wl(twofountains_wl$Depth.ft, 20/12)

# Save percentage of days water level is below outlet as variable
below_outlet_wl <- c(hospital_below_outlet_wl,lot60_below_outlet_wl,garner_below_outlet_wl,doba7_below_outlet_wl,owen_below_outlet_wl,hpchurch_below_outlet_wl,doba8_below_outlet_wl,midtown_below_outlet_wl,elver_below_outlet_wl,twofountains_below_outlet_wl,greentree_below_outlet_wl,mariondunn_below_outlet_wl,manitou_below_outlet_wl,madcity_below_outlet_wl,baxter_below_outlet_wl,doba22_below_outlet_wl,doba5_below_outlet_wl,doba4_below_outlet_wl,doorcreek_below_outlet_wl,commave_below_outlet_wl)
```

Range of water levels that encompasses 50% of data in each pond
```{r}
# Function for water levels between 25th and 75th percentile
get_wl_range_25_75 <- function(pond_wl) {
  quantile_25 <- quantile(pond_wl, 0.25)
  quantile_75 <- quantile(pond_wl, 0.75)
  wl_range <- quantile_75 - quantile_25
  return(wl_range)
}

# Apply function to each pond
baxter_range_25_75 <- get_wl_range_25_75(baxter_wl$Depth.ft)
commave_range_25_75 <- get_wl_range_25_75(commave_wl$Depth.ft)
doba4_range_25_75 <- get_wl_range_25_75(doba4_wl$Depth.ft)
doba5_range_25_75 <- get_wl_range_25_75(doba5_wl$Depth.ft)
doba7_range_25_75 <- get_wl_range_25_75(doba7_wl$Depth.ft)
doba8_range_25_75 <- get_wl_range_25_75(doba8_wl$Depth.ft)
doba22_range_25_75 <- get_wl_range_25_75(doba22_wl$Depth.ft)
doorcreek_range_25_75 <- get_wl_range_25_75(doorcreek_wl$Depth.ft)
elver_range_25_75 <- get_wl_range_25_75(elver_wl$Depth.ft)
garner_range_25_75 <- get_wl_range_25_75(garner_wl$Depth.ft)
greentree_range_25_75 <- get_wl_range_25_75(na.omit(greentree_wl$Depth.ft))
hospital_range_25_75 <- get_wl_range_25_75(hospital_wl$Depth.ft)
hpchurch_range_25_75 <- get_wl_range_25_75(na.omit(hpchurch_wl$Depth.ft))
lot60_range_25_75 <- get_wl_range_25_75(lot60_wl$Depth.ft)
madcity_range_25_75 <- get_wl_range_25_75(madcity_wl$Depth.ft)
manitou_range_25_75 <- get_wl_range_25_75(na.omit(manitou_wl$Depth.ft))
mariondunn_range_25_75 <- get_wl_range_25_75(mariondunn_wl$Depth.ft)
midtown_range_25_75 <- get_wl_range_25_75(midtown_wl$Depth.ft)
owen_range_25_75 <- get_wl_range_25_75(owen_wl$Depth.ft)
twofountains_range_25_75 <- get_wl_range_25_75(twofountains_wl$Depth.ft)

# Save water level range between 25 and 75 quantile as variable
wl_range_25_75 <- c(hospital_range_25_75,lot60_range_25_75,garner_range_25_75,doba7_range_25_75,owen_range_25_75,hpchurch_range_25_75,doba8_range_25_75,midtown_range_25_75,elver_range_25_75,twofountains_range_25_75,greentree_range_25_75,mariondunn_range_25_75,manitou_range_25_75,madcity_range_25_75,baxter_range_25_75,doba22_range_25_75,doba5_range_25_75,doba4_range_25_75,doorcreek_range_25_75,commave_range_25_75)
```

Range of water levels that encompasses 10 to 90% of data in each pond
```{r}
# Function for water levels between 10th and 90th percentile
get_wl_range_10_90 <- function(pond_wl) {
  quantile_10 <- quantile(pond_wl, 0.1)
  quantile_90 <- quantile(pond_wl, 0.9)
  wl_range <- quantile_90 - quantile_10
  return(wl_range)
}

# Apply function to each pond
baxter_range_10_90 <- get_wl_range_10_90(baxter_wl$Depth.ft)
commave_range_10_90 <- get_wl_range_10_90(commave_wl$Depth.ft)
doba4_range_10_90 <- get_wl_range_10_90(doba4_wl$Depth.ft)
doba5_range_10_90 <- get_wl_range_10_90(doba5_wl$Depth.ft)
doba7_range_10_90 <- get_wl_range_10_90(doba7_wl$Depth.ft)
doba8_range_10_90 <- get_wl_range_10_90(doba8_wl$Depth.ft)
doba22_range_10_90 <- get_wl_range_10_90(doba22_wl$Depth.ft)
doorcreek_range_10_90 <- get_wl_range_10_90(doorcreek_wl$Depth.ft)
elver_range_10_90 <- get_wl_range_10_90(elver_wl$Depth.ft)
garner_range_10_90 <- get_wl_range_10_90(garner_wl$Depth.ft)
greentree_range_10_90 <- get_wl_range_10_90(na.omit(greentree_wl$Depth.ft))
hospital_range_10_90 <- get_wl_range_10_90(hospital_wl$Depth.ft)
hpchurch_range_10_90 <- get_wl_range_10_90(na.omit(hpchurch_wl$Depth.ft))
lot60_range_10_90 <- get_wl_range_10_90(lot60_wl$Depth.ft)
madcity_range_10_90 <- get_wl_range_10_90(madcity_wl$Depth.ft)
manitou_range_10_90 <- get_wl_range_10_90(na.omit(manitou_wl$Depth.ft))
mariondunn_range_10_90 <- get_wl_range_10_90(mariondunn_wl$Depth.ft)
midtown_range_10_90 <- get_wl_range_10_90(midtown_wl$Depth.ft)
owen_range_10_90 <- get_wl_range_10_90(owen_wl$Depth.ft)
twofountains_range_10_90 <- get_wl_range_10_90(twofountains_wl$Depth.ft)

# Save water level range between 10 and 90 quantile as variable
wl_range_10_90 <- c(hospital_range_10_90,lot60_range_10_90,garner_range_10_90,doba7_range_10_90,owen_range_10_90,hpchurch_range_10_90,doba8_range_10_90,midtown_range_10_90,elver_range_10_90,twofountains_range_10_90,greentree_range_10_90,mariondunn_range_10_90,manitou_range_10_90,madcity_range_10_90,baxter_range_10_90,doba22_range_10_90,doba5_range_10_90,doba4_range_10_90,doorcreek_range_10_90,commave_range_10_90)
```

Skewness of pdfs
```{r}
library(moments)

# Find skewness for each pond
baxter_skew <- skewness(baxter_wl$Depth.ft)
commave_skew <- skewness(commave_wl$Depth.ft)
doba4_skew <- skewness(doba4_wl$Depth.ft)
doba5_skew <- skewness(doba5_wl$Depth.ft)
doba7_skew <- skewness(doba7_wl$Depth.ft)
doba8_skew <- skewness(doba8_wl$Depth.ft)
doba22_skew <- skewness(doba22_wl$Depth.ft)
doorcreek_skew <- skewness(doorcreek_wl$Depth.ft)
elver_skew <- skewness(elver_wl$Depth.ft)
garner_skew <- skewness(garner_wl$Depth.ft)
greentree_skew <- skewness(na.omit(greentree_wl$Depth.ft))
hospital_skew <- skewness(hospital_wl$Depth.ft)
hpchurch_skew <- skewness(hpchurch_wl$Depth.ft)
lot60_skew <- skewness(lot60_wl$Depth.ft)
madcity_skew <- skewness(madcity_wl$Depth.ft)
manitou_skew <- skewness(manitou_wl$Depth.ft)
mariondunn_skew <- skewness(mariondunn_wl$Depth.ft)
midtown_skew <- skewness(midtown_wl$Depth.ft)
owen_skew <- skewness(owen_wl$Depth.ft)
twofountains_skew <- skewness(twofountains_wl$Depth.ft)

# Save skewness as variable
pond_skewness <- c(hospital_skew,lot60_skew,garner_skew,doba7_skew,owen_skew,hpchurch_skew,doba8_skew,midtown_skew,elver_skew,twofountains_skew,greentree_skew,mariondunn_skew,manitou_skew,madcity_skew,baxter_skew,doba22_skew,doba5_skew,doba4_skew,doorcreek_skew,commave_skew)
```

Water Level Variance
```{r}
# Find variance for each pond
baxter_var <- var(baxter_wl$Depth.ft)
commave_var <- var(commave_wl$Depth.ft)
doba4_var <- var(doba4_wl$Depth.ft)
doba5_var <- var(doba5_wl$Depth.ft)
doba7_var <- var(doba7_wl$Depth.ft)
doba8_var <- var(doba8_wl$Depth.ft)
doba22_var <- var(doba22_wl$Depth.ft)
doorcreek_var <- var(doorcreek_wl$Depth.ft)
elver_var <- var(elver_wl$Depth.ft)
garner_var <- var(garner_wl$Depth.ft)
greentree_var <- var(na.omit(greentree_wl$Depth.ft))
hospital_var <- var(hospital_wl$Depth.ft)
hpchurch_var <- var(hpchurch_wl$Depth.ft)
lot60_var <- var(lot60_wl$Depth.ft)
madcity_var <- var(madcity_wl$Depth.ft)
manitou_var <- var(manitou_wl$Depth.ft)
mariondunn_var <- var(mariondunn_wl$Depth.ft)
midtown_var <- var(midtown_wl$Depth.ft)
owen_var <- var(owen_wl$Depth.ft)
twofountains_var <- var(twofountains_wl$Depth.ft)

# Save variance as variable
pond_var <- c(hospital_var,lot60_var,garner_var,doba7_var,owen_var,hpchurch_var,doba8_var,midtown_var,elver_var,twofountains_var,greentree_var,mariondunn_var,manitou_var,madcity_var,baxter_var,doba22_var,doba5_var,doba4_var,doorcreek_var,commave_var)

```

Save all variables in csv file
```{r}
# Pond names
pond_names <- c("Hospital", "Lot60", "Garner", "DobA7", "Owen", "HPChurch", "DobA8", "Midtown", "Elver", "TwoFountains", "Greentree", "MarionDunn", "Manitou", "MadCity", "Baxter", "DobA22", "DobA5", "DobA4", "DoorCreek", "CommAve")

# Create a data frame for all ponds
constant_depth_df <- data.frame(Pond.Names = pond_names, Median.Water.Level = median_wl, Constant.Water.Level = constant_wl, Contant.Water.Level.6in = constant_wl_6in, Outlet.Water.Level = outlet_wl, Below.Outlet.Water.Level = below_outlet_wl, Water.Level.25.75.Quantile = wl_range_25_75, Water.Level.10.90.Quantile = wl_range_10_90, Pond.Skewness = pond_skewness, Pond.Variance = pond_var)

# Write csv for data frame
write.csv(constant_depth_df, "/Users/hannahcurtis/Desktop/School/UWMadison/Research/Data Analysis/Predictor_Variables/Constant_Depth/Uniform_Depth_all.csv")
```
